Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-11-16 paper/paper.tex
sketch of path length 3 example added.
Ref figure, and reorder hackery for now

\begin{figure*}[t]
    \centering
    \includegraphics*{gen-graph-constraints-induced-0.pdf}
    \includegraphics*{gen-graph-constraints-induced-1.pdf}
    \includegraphics*{gen-graph-constraints-induced-2.pdf}
    \includegraphics*{gen-graph-constraints-induced-3.pdf}
    \includegraphics*{gen-graph-constraints-induced-4.pdf}
    \includegraphics*{gen-graph-constraints-induced-5.pdf}

@@

Unlike in conventional subgraph isomorphism, we cannot extend this filtering to look at paths of
length three: removing a single vertex can delete arbitrarily many such paths. We \emph{could}
instead count paths of any length which are vertex disjoint, although calculating this appears to be
too expensive to be beneficial in practice.

@@

>>>>

@@

Unlike in conventional subgraph isomorphism, we cannot extend this filtering to look at paths of
length three: as the example in \cref{figure:pathlength3example} shows, removing a single vertex can
delete arbitrarily many such paths. We \emph{could} instead count paths of any length which are
vertex disjoint, although calculating this appears to be too expensive to be beneficial in practice.

\begin{figure}[tb]
    \centering
    \begin{tikzpicture}[scale=0.5]%[every node/.style={circle, inner sep=0.5mm,node
        %distance=10mm,fill=black}, scale=0.2]

@@

\begin{figure*}[tb]
    \centering
    \includegraphics*{gen-graph-constraints-induced-0.pdf}
    \includegraphics*{gen-graph-constraints-induced-1.pdf}
    \includegraphics*{gen-graph-constraints-induced-2.pdf}
    \includegraphics*{gen-graph-constraints-induced-3.pdf}
    \includegraphics*{gen-graph-constraints-induced-4.pdf}
    \includegraphics*{gen-graph-constraints-induced-5.pdf}
